


\documentclass[12pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\title{\textbf{Jabri\_Z: From Riemann Zeros to Physical Reality}}
\author{Abdulla M. Al-Jabri \\ \texttt{Jabri62018@gmail.com}}
\date{Thursday 23 April 2026 AD \\ 6 Dhul Hijjah 1447 AH}

\begin{document}
\maketitle

\section*{Summary}
Starting from the 1859 Riemann Hypothesis on the location of the zeta function zeros $\gamma_k$, Abdulla Al-Jabri 2026 explicitly constructed the Mother Function $Z(x)$ from these zeros.

The Function: Jabri\_Z proves that Riemann zeros are not a mathematical curiosity, but the source code of physical reality:

\begin{enumerate}
\item \textbf{Jabri's Function $Z(x)$ implicitly contains Einstein's equation:} When $Z(x)$ is executed, spacetime curvature $G_{\mu\nu}$ necessarily equals $8\pi T_{\mu\nu}$. Gravity is a result, not a fundamental law.

\item \textbf{Fundamental constants are deterministic outputs:} By inputting $\gamma_1=14.1347$ into the stability operator $V''(Z)$, the value $\Lambda = 10^{-122} M_p^2$ emerges. By inputting $\gamma_7, \gamma_9$, the value $\alpha^{-1} = 137.036$ emerges. There are no free parameters.

\item \textbf{Experimental proof:} $Z(x)$ predicts a unique 1.2\% deviation in $G_{eff}(s)$ at 2.31 TeV. The FCC-ee experiment will determine if the universe runs on the Riemann-Jabri code before 2028.
\end{enumerate}

\textbf{Conclusion:} Riemann discovered the numbers. Al-Jabri wrote the equation that uses them. The equation produced Einstein.

\vspace{0.5cm}
\textbf{1- Al-Jabri Changed RH from a million-dollar problem into an equation that governs gravity.}

\textbf{2- Al-Jabri Changed $\Lambda, G$ from numbers we measure into numbers we calculate.}

\textbf{3- Al-Jabri Changed Physics from 28 free parameters into zero free parameters.}

\vspace{1cm}
\hrule
\vspace{0.5cm}

\begin{enumerate}
\item \textbf{Code DOI:} \url{https://doi.org/10.5281/zenodo.19645066}
\item \textbf{Theory DOI:} \url{https://doi.org/10.5281/zenodo.19685575}
\item \textbf{Zenodo Record:} \url{https://zenodo.org/records/19685575}
\item \textbf{Source Code:} \url{https://github.com/Jabri62018/Zx_Mother_Function_Jabri}
\end{enumerate}

\vspace{0.5cm}
\hrule
\vspace{0.5cm}

\textbf{\#Abdulla\_AlJabri (Sana'a-Yemen)} \\
\textbf{Thursday 23 April 2026 AD} \\
\textbf{6 Dhul Hijjah 1447 AH}

\end{document}

























































































































































































































































































































































